\documentclass[12pt]{article}

% Page layout
\usepackage{geometry}
\geometry{
  top=1in,
  bottom=1in,
  left=1in,
  right=1in,
  headheight=3ex,
  headsep=4ex,
}

% Header/footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\footrulewidth}{0.4pt}
\lhead{CSC311}
\rhead{Machine Learning Project}
\rfoot{Page \thepage}
\cfoot{v1.0}
\lfoot{\copyright Alice Gao 2025}

% Hyperlinks
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

% Colors (for environments)
\usepackage{xcolor}

% Formatting
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

% Custom environments
\newenvironment{answer}[1][]{
  \color{blue}\textbf{Answer:}
}{}

\newenvironment{alice}[1][]{
  \color{black}\textbf{Tip:}
}{}


\title{CSC311 Machine Learning Project Group Contract}
\author{}
\date{}


\begin{document}

\maketitle

This group contract helps you set and communicate your expectations for working together on the project. If any issues come up, the course staff will use this contract to help resolve them.

Discuss the following questions as a group and fill out the answers below.

\begin{enumerate}
\item {\bf Group Members:} Write down the full names of your group members and UTORids.

\begin{answer}

\begin{tabular}{|l|l|}
    \hline
    Name & UTORid \\
    \hline
    Leo Lei & leisong1 \\
    \hline
\end{tabular}

\end{answer}

\item {\bf Goals and Expectations} What does each member want to achieve from this project? Are your goals aligned as a group?

\begin{answer}

We are all aiming for an A/A+ on this project and strive to reach this goal with the best of our abilities. 

\end{answer}

\item {\bf Group Roles:} What roles are necessary for the success of your project? Who will be assigned to each role? Consider each member’s strengths and weaknesses.

\begin{answer}

Replace this with your answer.

\end{answer}

\item {\bf Communication:} How will you communicate? What are your expectations for response times? How often will you meet, and for how long? What technology will you use?

\begin{alice}

Schedule a mandatory weekly meeting to stay on track and address issues promptly.
\end{alice}

\begin{answer}

We will be using Discord to communicate. The expected response time should be at most a couple of hours. We plan on doing a weekly virtual meeting on Discord to keep everyone up to date and address any issues or difficulties. 

\end{answer}

\item {\bf Preparation for Meetings:} What should members do before each weekly meeting?

\begin{alice}

Create a list of to-do items at the end of each meeting and review them at the next meeting.

\end{alice}

\begin{answer}

Replace this with your answer.
\end{answer}


\item {\bf Meeting Conduct:} What are your expectations for attitudes and responses during meetings? How will you manage turn-taking and ensure everyone contributes? How will you make decisions?

\begin{answer}

Replace this with your answer.
\end{answer}

\begin{alice}

Structure meetings effectively and decide on a method for resolving disagreements, such as consensus or majority vote.
\end{alice}

\item {\bf Work Structure:} How will you structure the work? Will most of it be done during or outside of meetings? How will you assign responsibilities?

\begin{answer}

Replace this with your answer.
\end{answer}

\begin{alice}

Use a divide-and-conquer approach, ensuring an equal workload for all members.
\end{alice}

\item {\bf Submission of Deliverables:} How will you submit deliverables? Will all members review the submission before it’s finalized? When should the write-up be ready for review?

\begin{answer}

Replace this with your answer.
\end{answer}

\begin{alice}

Communicate struggles early and work together to find solutions.
\end{alice}

\item {\bf Handling Surprises:} How will you deal with unexpected challenges? What should a member do if they can’t deliver on a promise? How will the group respond?

\begin{answer}

Replace this with your answer.
\end{answer}

\begin{alice}

Communicate struggles early and work together to find solutions.
\end{alice}

\item {\bf Conflict Resolution:} How will you handle conflicts? How can a member signal an issue? How will the group respond?

\begin{answer}

If a member can't deliver on a promise, they should mention in advance so the team has time to respond. Possible resolution includes assigning parts of the work to another member and possibly adjusting the timeline. 

\end{answer}

\begin{alice}

Establish a protocol for resolving conflicts and seek help from course staff if needed.
\end{alice}

\end{enumerate}

\end{document}





























